Understanding domestic abuse - Pathways to Impact

### 2019-07-23 pathways_to_impact.tex
Anna update

The research proposed here has been developed with direct input from officers and experts within WMP. This has allowed us to design the research questions that are relevant to current issues within WMP, and that can feed in to existing structures to accelerate the dissemination of findings, and changes in policy. To facilitate this, we have a day-to-day contact at WMP: Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning), and within the West Midlands Police and Crime Commissioner's Office, Alison Spence. As a result of this close collaboration, we have received support from senior levels within WMP including from Deputy Chief Constable Louisa Rolfe who is the National Police Chiefs Council lead for domestic abuse.

>>>>

The research proposed here has been developed with direct input from officers and experts within WMP. This has allowed us to design the research questions that are relevant to current issues within WMP, and that can feed in to existing structures to accelerate the dissemination of findings, and changes in policy. To facilitate this, we have a day-to-day contact at WMP: Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning), and within the WMP and Crime Commissioner's Office, Alison Spence. As a result of this close collaboration, we have received support from senior levels within WMP including from Deputy Chief Constable Louisa Rolfe who is the National Police Chiefs Council lead for domestic abuse.
